\section{Error Analysis and Discussion}
The main sources of error in this work are likely related to
measurement setup and sensor behavior. Larger
deviations appear mainly at short distances and at a few isolated
outlier points, suggesting that the error is not caused by one factor
alone.

One possible source is human error during measurement and calibration.
Small inaccuracies in setting the reference distance, reading the scale,
or entering the calibration value into the firmware may affect the
calculated correction factor. Parallel alignment error between the
sensor and the target surface may also influence the time-of-flight by
changing the effective reflection path.

Environmental conditions may also contribute to the observed
differences. Since the speed of sound depends on temperature and
humidity, variations in the surrounding air can affect the measured
distance. In this work, these effects were handled mainly through
calibration, and they could be reduced further by incorporating
additional environmental sensors in future implementations. Unwanted
reflections, acoustic disturbance, and nearby obstacles may also
introduce noise into the received signal.

Sensor and circuit limitations may be another reason for the remaining
error. Timing jitter, inconsistent echo detection, or reduced response
stability at some distances may produce abnormal samples. This may
explain why some moving-average results become worse when outliers are
present.

The clearance results also suggest a practical geometric limitation.
Although the system was able to detect distance up to 165~cm, the
required clearance increases with distance because of beam spreading. A
theoretical measurement angle of about $15^\circ$ appears to be
reasonable only within the first 30~cm, while the experimental pattern
after that region is closer to about $22^\circ$. If a maximum allowable
clearance of 30~cm is imposed in the path of flight, the practical
usable range would be limited to approximately 90~cm even though the
sensor can still detect targets beyond that distance.

Thus, the observed errors may be associated with a combination of human
measurement uncertainty, parallel alignment error, environmental
variation, and sensor noise. Other factors may also be present in the
experimental setup. For this reason, the present system may be less
appropriate for precision-critical applications, while remaining
practically useful in tasks where an uncertainty of roughly
$\pm 0.45$~cm is acceptable.
