\section{Measurement Principle}

Ultrasonic distance measurement operates on the principle of
time-of-flight (ToF) of an acoustic pulse. A short burst of
high-frequency sound (typically around 40\,kHz) is emitted
toward the target object. The sensor then switches to receive
mode and measures the elapsed time until the reflected echo
returns from the object.

\subsection{Time-of-Flight Principle}

Because the ultrasonic pulse travels from the sensor to the
target and back again, the one-way distance $d$ can be
determined from the measured round-trip time $t$. The
relationship between distance and travel time is given by

\begin{equation}
d = \frac{c\,t}{2}
\end{equation}

where $c$ represents the speed of sound in air and $t$
is the measured echo return time. The factor $\frac{1}{2}$
accounts for the two-way propagation path of the ultrasonic
pulse.

This principle is commonly used in pulse-echo ultrasonic
sensors such as the HC-SR04 module, where the same
transducer emits the ultrasonic pulse and detects the
reflected signal.

\subsection{Speed of Sound in Air and Environmental Compensation}

The speed of sound in air depends primarily on the ambient
temperature. In dry air at $0^\circ$C, the speed of sound is
approximately

\begin{equation}
c \approx 331.45 \; \mathrm{m\,s^{-1}}
\end{equation}

A commonly used linear approximation relating sound speed
to air temperature is \cite{mi13040520}

\begin{equation}
c \approx 331.45 + 0.607\,T_C
\end{equation}

where $T_C$ is the air temperature in degrees Celsius. This
relation indicates that the speed of sound increases by about
$0.6\,\mathrm{m\,s^{-1}}$ for every $1^\circ$C increase in
temperature.

Environmental factors such as humidity and atmospheric
pressure also affect the propagation speed of sound, though
their influence is comparatively smaller. Across typical
ranges of $0$--$100\%$ relative humidity and
$50$--$110$\,kPa pressure, the variation in sound speed is
generally less than $0.7\%$ \cite{mi13040520}.

For improved measurement accuracy, the ESP32 can update
distance calculations using a temperature-dependent value
of $c$. By incorporating temperature readings during
operation, systematic errors caused by environmental
variations can be reduced.