\section{Methodology and Design}
\subsection{Hardware Implementation}

The prototype consists of the following main components:

\begin{itemize}
\item ESP32 development board
\item HC-SR04 ultrasonic sensor
\item Low-power laser module mounted at the centerline of the ultrasonic transducers
\item I\textsuperscript{2}C 16$\times$2 LCD module with backpack
\item Breadboard, jumper wires, and regulated power supply
\end{itemize}

\subsubsection{Circuit Connections}

The ESP32 development board is powered using a regulated 3.3\,V supply.
The ultrasonic sensor module is powered from the ESP32 supply rail, and
its ground is connected to the ESP32 ground to establish a common reference.

The Trigger pin of the ultrasonic sensor is connected to a digital GPIO pin
configured as an output. The Echo pin is connected to a GPIO pin
configured as an input.

The I\textsuperscript{2}C LCD module is connected to the ESP32
I\textsuperscript{2}C interface. The SDA and SCL lines are connected
to GPIO 21 and GPIO 22 respectively.

The laser module is mechanically fixed so that its beam emerges from the
middle of the two ultrasonic transducers. This laser is used only as a
visual pointer to align the measurement axis with the target point.

\subsubsection{Prototype Assembly}

All components are assembled on a breadboard during the prototyping stage.
The ultrasonic transducer is positioned so that it has a clear line of sight
to the target surface. The laser pointer is adjusted during assembly so its
spot coincides with the center of the ultrasonic sensing direction.
Care is taken to minimize nearby reflective objects that could introduce
unwanted echoes. If necessary, simple shielding or damping materials can be
placed around the sensor to reduce acoustic reflections from surrounding
surfaces.

\subsection{Software Flow}
The ESP32 generates a trigger pulse sequence for each measurement cycle.
First, the trigger pin is set LOW for $2\,\mu$s, then set HIGH for
$10\,\mu$s, and then returned LOW. The echo pulse width is measured using the
Arduino \texttt{pulseIn()} function on the echo pin with a timeout of
$30{,}000\,\mu$s. The detailed software and firmware implementation used
in this project is available in the project repository
\cite{eee354_github_repo}.

If no valid echo pulse is received within the timeout, that cycle is ignored.
If a valid pulse is received, the time value is stored and the distance is
computed using Eq.~(3). The resulting distance is then sent to the active user
interface mode.

Two software operating modes are implemented:
\begin{itemize}
\item \textbf{LCD mode (local mode):} after powering the ESP32, pressing the
BOOT button once starts local display mode, where distance is shown on the
LCD.
\item \textbf{Website mode (Wi-Fi mode):} after reset, pressing the BOOT
button twice starts web mode. The ESP32 starts the web interface and displays
its IP address. A user connects over Wi-Fi, opens the IP address in a browser,
and can view live readings, record readings, and perform calibration tasks
\cite{eee354_github_repo}.
\end{itemize}
